### 2016-09-23 capability-machine.tex
Fix mistake.

The simplest thing that comes to mind as a formal result for all of the above is
to look at a concrete program that clearly relies on properties like
well-bracketed control flow and encapsulation of local variables and prove it
correct. As a concrete example: we might show an assembly program that
corresponds to the following (a higher-order program that crosses trust
boundaries and relies on local variable encapsulation and well-bracketed control
flow):
\begin{verbatim}
let trustedCode = fun adversary =>
                    let x = ref 0 in
                    let callback = fun adv2 => 
                      let y = ref (!x) in 
                      assert (!x >= 0); 
                      x := -1; 
                      c2 unit; 
                      x := !y)
                    let _ = adversary callback
                    assert (!x >= 0)
\end{verbatim}
\lau{I have inserted some line breaks for readability. I am not sure what is going on here (the parenthesis after y is unmatched.)}
\section{Related reading}
\label{sec:related-reading}

>>>>

The simplest thing that comes to mind as a formal result for all of the above is
to look at a concrete program that clearly relies on properties like
well-bracketed control flow and encapsulation of local variables and prove it
correct. As a concrete example: we might show an assembly program that
corresponds to the following (a higher-order program that crosses trust
boundaries and relies on local variable encapsulation and well-bracketed control
flow):
\begin{verbatim}
let trustedCode = fun adversary =>
                    let x = ref 0 in
                    let callback = fun adv2 => 
                      let y = ref (!x) in 
                      assert (!x >= 0); 
                      x := -1; 
                      adv2 unit; 
                      x := !y)
                    let _ = adversary callback
                    assert (!x >= 0)
\end{verbatim}
\lau{I have inserted some line breaks for readability. I am not sure what is going on here (the parenthesis after y is unmatched.)}
\section{Related reading}
\label{sec:related-reading}
